---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Sairam Kumaran"
date: "29 September 2023"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r}
#install.packages("dplyr")
#install.packages("tidymodels")
#install.packages("gt")
#install.packages("gtExtras")
library(magrittr)     # the pipe
library(tidyverse) 
library(dplyr)
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

### Exercise 1

```{r}
dplyr::distinct(the_tate,artist)

min(the_tate$year,na.rm = T)
max(the_tate$year,na.rm = T)
min(the_tate$acquisitionYear,na.rm = T)
max(the_tate$acquisitionYear,na.rm = T)
```

The `the_tate` dataset has [3336]{.underline} unique artists who worked from 1545 to 2012. The works were acquired between the years 1823 and 2013.

### Exercise 2

```{r}
missing_work <- the_tate |> dplyr::filter(is.na(year))
missing_work
dplyr::distinct(missing_work,title)
dplyr::distinct(missing_work,artist)
```

```{r}
missing_works <- table(the_tate$title[is.na(the_tate$year)])
#mw <- missing_works['TRUE']
count_titles_with_missing_dates <- length(missing_works)
count_titles_with_missing_dates

missing_artists <- table(the_tate$artist[is.na(the_tate$year)])
#mw <- missing_works['TRUE']
count_titles_with_missing_dates <- length(missing_artists)
count_titles_with_missing_dates
```

```{r}

#missing_works_table <- dplyr::filter(the_tate,is.na(the_tate$year))
#missing_works_table
#missing_works_table_2 <- table(missing_works_table$title)
#print(missing_works_table_2)
#missing_works_df <- as.data.frame(missing_works_table_2)
#missing_works_tibble <- as_tibble(missing_works_table_2)
#missing_works_tibble <- missing_works_tibble %>%
 # arrange(desc(Freq))
#missing_works_tibble
```

How number of works with missing dates is 2583.

The number of artists whose works have missing dates is 461\_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

### Exercise 3

```{r}
artist_counts <- the_tate %>%
  group_by(artist) %>%
  summarize(work_count = n()) %>%
  arrange(desc(work_count))
artist_counts[1,]
artist_counts[10,"work_count"]
```

The artist with the most works in the Tate collection is Turner, Joseph Mallord\_\_\_.

The artist with the tenth-most works in the Tate collection is Warhol, Andy\_\_\_.

### Exercise 4

```{r}
top_g = (artist_counts[1,"work_count"]/count(the_tate)['n'])*100
top_g
```

The artist with the greatest number of works in the Tate collection represent 56.9197% of the total number of works

### Exercise 5

```{r}
duplicate_pairs <- the_tate[duplicated(the_tate[c("artist", "title")]) | duplicated(the_tate[c("artist", "title")], fromLast = TRUE), ]
#duplicate_pairs[c("artist","title")]
duplicate_count <- nrow(duplicate_pairs)
duplicate_count
```

There are [29021]{.underline} duplicate artist-title pairs

### Exercise 6

```{r}
artist_counts[1,"artist"]
least_A = tail(artist_counts,n=1)
tmp = least_A[1,1]
tmp
filtered_data <- the_tate %>%
  filter(artist == "di Suvero, Mark")
(filtered_data["width"]/10)*(filtered_data["height"]/10)
```

The artist with the largest work in the tate collection is Turner, Joseph Mallord\_\_\_

The artist with the smallest work in the collection is di Suvero, Mark. The smallest work has area \_9711.36 $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
